Gaudeamus 2017 Figures

### 2018-02-15 inst/examples/201705-Gaudeamus.Rmd
Gaudeamus polish

---
title: "Gaudeamus 2017 Figures"
author: "Mikko Tolonen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation
fontsize: 13pt
---

@@

# Default time span
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
knitr::opts_chunk$set(echo = FALSE)
# knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/")
##knitr::opts_chunk$set(fig.path = "slides_201606_Krakow", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoJPEG")

@@

```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS(input.data.file)
# Data with duplicates removed and years limited

min.year <- 1488
max.year <- 1828
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
       geom_point() + 
       geom_line() + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
print(p)
```

@@

```{r Gaudeamus-3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=13, dev="CairoJPEG"}
theme_set(theme_bw(22))
pics <- list()
for (catal in unique(df0$catalog)) {
  df2 <- df0 %>% filter(catalog == catal) %>% 
                 group_by(publication_decade, gatherings) %>% 
		 summarise(paper2 = sum(paper, na.rm = TRUE)/1e6, n = n()) 
  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

@@

```{r Gaudeamus-Vaasa, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))

@@

```{r Gaudeamus-Turku, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Turku") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Helsinki, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1740) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Helsinki") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Suomi, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%	       
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed
df2$publication_place[!df2$publication_place %in% c("Helsinki", "Turku", "Vaasa")] <- "Muu"
df2 <- df2 %>%
       	       filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) 
p <- ggplot(df2, aes(x = publication_decade)) +
   geom_bar(position = "stack", aes(y = ..count.., fill = publication_place), color = "black") +
   scale_fill_grey() +   
   xlab("Vuosi") +
   ylab("Dokumenttia (n)") +
   scale_x_continuous(breaks = c(1640, 1764, 1809, 1863, 1917),
     	              labels = c(1640, 1764, 1809, 1863, 1917)) +
   guides(fill = guide_legend(keywidth=1, title = "Julkaisupaikka")) +
   theme(legend.position = c(0.16, .7)) 
print(p)
```

>>>>

---
title: "Gaudeamus 2017 Figures"
author: "Mikko Tolonen, Leo Lahti"
date: "`r Sys.Date()`"
output:
  beamer_presentation:
    dev: cairo_pdf  
  pdf_document:
    dev: cairo_pdf
    keep_tex: yes
fontsize: 13pt
---

@@

# Default time span
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
knitr::opts_chunk$set(echo = FALSE)
# knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/")
# knitr::opts_chunk$set(fig.path = "slides_201606_Krakow", dev="CairoPNG")
# knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoJPEG")
knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoPDF")

@@

```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS(input.data.file)
# Data with duplicates removed and years limited
min.year <- 1488
max.year <- 1828
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

@@

```{r Gaudeamus-lineplot, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
       geom_point() + 
       geom_line() + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
print(p)

```

@@

```{r Gaudeamus-3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=13, dev="CairoPDF"}
theme_set(theme_bw(22))
pics <- list()
for (catal in unique(df0$catalog)) {
  df2 <- df0 %>% filter(catalog == catal) %>% 
                 group_by(publication_decade, gatherings) %>% 
		 summarise(paper2 = sum(paper, na.rm = TRUE)/1e6, n = n()) 
  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

@@

```{r Gaudeamus-Vaasa, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
library(dplyr)
theme_set(theme_bw(22))

@@

```{r Gaudeamus-Turku, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Turku") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Helsinki, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1740) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Helsinki") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Suomi, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%	       
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

@@

```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed
df2$publication_place[!df2$publication_place %in% c("Helsinki", "Turku", "Vaasa")] <- "Muu"
df2 <- df2 %>%
       	       filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) 
p <- ggplot(df2, aes(x = publication_decade)) +
   geom_bar(position = "stack", aes(y = ..count.., fill = publication_place), color = "black") +
   scale_fill_grey() +   
   xlab("Vuosi") +
   ylab("Dokumenttia (n)") +
   scale_x_continuous(breaks = c(1640, 1764, 1809, 1863, 1917),
     	              labels = c(1640, 1764, 1809, 1863, 1917)) +
   guides(fill = guide_legend(keywidth=1, title = "Julkaisupaikka")) +
   theme(legend.position = c(0.16, .7)) 
print(p)

library(tidyr)
table_hs <- df2 %>% group_by(publication_decade, publication_place) %>%
                    tally() %>%
		    spread(publication_place, n, fill = 0)
library(openxlsx)		    
# openxlsx::write.xlsx(table_hs, file = "Table_HS_20180107.xlsx")
```
